Global Optimization of the Analogue Method by Means of Genetic Algorithms

### 2015-10-29 AtmoSwing - Geoscientific Model Development/template.tex
Editing the GAs section.

\section{Genetic algorithms}
\label{sec:gas}

@@

@@

	$N\approx500$ for significantly more complex AMS (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),

@@

\begin{acknowledgements}
Thanks to Lucien Schreiber and Richard Metzger for their programming advices. Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base.

>>>>

\section{Optimization using Genetic algorithms}
\label{sec:gas}

@@

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}
	\caption{Genetic algorithms operational flowchart}
	\label{fig:structure_gas}
\end{figure}

@@

	$N\approx500$ for significantly more complex AMs (2-3 levels of analogy with 4 pressure levels for the atmospheric circulation, and 2 to 4 levels for the moisture analogy),

@@

\begin{acknowledgements}
Thanks to Lucien Schreiber and Richard Metzger for their programming advices. Thanks to Renaud Marty for his active involvement in testing AtmoSwing against his code base. Thanks to Hamid Hussain-Khan of the University of Lausanne for his help and availability, and for the intensive use of the cluster he is in charge of.

### 2015-10-29 Optimization - Journal of Climate/template.tex
Editing the GAs section.

@@

\begin{figure}[htb]
	\centerline{\includegraphics[width=7.9cm]{figures/figure_structure_gas.pdf}}
	\caption{Genetic algorithms operational flowchart}
	\label{fig:structure_gas}
\end{figure}

>>>>

\section{Genetic algorithms}

%TODO: write this section

Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}. It is indeed mainly a matter of time. When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}. For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time. Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}. This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.

@@
